### 2013-10-02 Paper_Markdown.Rmd
Expanded introductory text to introduce method outline.  Revised plotting of model-exclusion ghostplots, improved figure caption for the ghostplots.  Also fixed the MAT bootstrap to run for July temperatures and to run a lower number of quantiles given preliminary outputs.

Although we cannot know the values for temperature or

@@

ggplot(na.samples, aes(x=distance, y=size, group )) + 
  geom_path(aes(alpha=alpha.val)) +
  xlab('Analogue Distance') + ylab('Available Samples') +
  theme(text = element_text(size=24, family='serif')) +
  theme_bw() +
  scale_alpha_identity(guide='none')

@@

ggplot(model.out, aes(x = dissim, y = preds, group = site)) +
  geom_path(alpha = 0.01) +
  theme_bw() +
  facet_wrap(~mode)
  scale_x_continuous(expand=c(0,0)) +
  annotate('segment', x=0, xend=1, 
           y=mean(climate[,10], na.rm=TRUE),
           yend=mean(climate[,10], na.rm=TRUE),
           color='red', size=1.5, linetype=2)

```
**Figure X**.

>>>>

Although we cannot know the values for temperature or precipitation during this time, statistical non-analogues do exist in a modern context, and we can construct false non-analogues using a modified h-block sampling procedure

@@

ggplot(na.samples, aes(x=distance, y=size)) + 
  geom_path(aes(group=site), alpha=0.001) +
  xlab('Analogue Distance') + ylab('Available Samples') +
  theme(text = element_text(size=24, family='serif')) +
  theme_bw()

@@

ggplot(model.out, aes(x = dissim, y = preds, group = site)) +
  geom_path(alpha = 0.01) +
  theme_bw() +
  facet_wrap(~model, scales='free_y') +
  scale_x_continuous(expand=c(0,0))

```
**Figure X**. *Change in site predictions over time.  Of great interest is the difference between model outputs as the exclusion zone increases.  MAT can never predict beyond the extent of the data samples in the pool, and so as the exclusion zone increases the predictions move toward the dataset mean.  WAPLS uses an initial transformation and then regresses against it to predict new values, so as the exclusion zone increases we see an increase in the spread of the predicted values, with much greater variability and a loss of accuracy.*

Discussion
=========================
What does this tell us about predicting climate in non-analogue space?
